6.867 Problem Set 3

### 2015-11-11 HW3/tex/HW3.tex
[hw3] prettify tables.

\begin{equation}
\frac{\partial J(w)}{\partial w_{jd}^{(1)}} = -\left ( \sum_{i=1}^N x_i \sum_{k=1}^{K} \left(y_k^{(i)}(1-\sigma(a_k^{(2)}) + (1-y_k^{(i)})(\sigma(a_k^{(2)})\right) w_{kj}^{(2)} \left(\frac{1}{1+e^{-a_{jd}^{(1)}}}\right)\left(1-\frac{1}{1+e^{-a_{jd}^{(1)}}}\right)\right ) + 2 \lambda w_{jd}^{(1)}.
\end{equation}

>>>>

\begin{equation}
\frac{\partial J(w)}{\partial w_{jd}^{(1)}} =  \sum_{i=1}^N x_i \sum_{k=1}^{K} \left(\sigma(a_k^{(2)}) -y_k^{(i)}\right) w_{kj}^{(2)} \left(\frac{1}{1+e^{-a_{jd}^{(1)}}}\right)\left(1-\frac{1}{1+e^{-a_{jd}^{(1)}}}\right) + 2 \lambda w_{jd}^{(1)}.
\end{equation}

Let's now see how a neural network performs on two different toy data sets. We vary both the number of hidden nodes and the regularization parameter in our objective function, and use both full gradient descent and batch gradient descent. The two algorithms perform comparably - in the case of toy data set number 2, we find that the full gradient descent algorithm does a slightly better job at finding the optimal values of our parameter than stochastic gradient descent (classification error of 6.7\% as opposed to 9\%). Our changes in parameters have a much larger effect on the performance for toy dataset 2 than for our features in toy dataset 1. This is likely due to the lack of an easy way to separate examples of different classes in dataset 2.

\begin{figure}[ht]
	\centering
	\begin{minipage}[b]{.48\linewidth}
		\includegraphics[width=1\linewidth, height=2.7in]{t1dist.jpg}
		\caption*{Toy Dataset \#1}
	\end{minipage}
	\begin{minipage}[b]{.48\linewidth}
		\includegraphics[width=1\linewidth, height=2.7in]{t2dist.jpg}
		\caption*{Toy Dataset \#2}
	\end{minipage}
	\caption{Distributions of different classes in $X1$, $X2$ for toy datasets}
\end{figure}

\begin{table}
\captionof{table}{Neural Network Classification Error Rates With Various Parameters on Toy Datasets} 
\centering
\begin{tabular}{llllllll}
\toprule
Dataset & Method & $\lambda$ & $n_1$ = \bf{1} & $n_1$ =  \bf{3} & $n_1$ =  \bf{5} & $n_1$ =  \bf{7} & $n_1$ =  \bf{9} \\
\midrule
Toy Dataset 1 (Training) & full gradient descent & 0 &     0.007 & \bf{0}     & 0     & 0     & 0     \\
Toy Dataset 1 (Training) & full gradient descent & 1e-5 &   0.007 & 0     & 0     & 0     & 0     \\
Toy Dataset 1 (Training) & full gradient descent & 1e-3 &  0.093 & 0.003 & 0.003 & 0.003 & 0.003 \\
Toy Dataset 1 (Training) & full gradient descent & 1e-1 &  0.667 & 0.667 & 0.667 & 0.667 & 0.667 \\
\midrule
Toy Dataset 1 (Validation) & full gradient descent & 0 &      0.01  & \bf{0.003} & 0.003 & 0.003 & 0.003 \\
Toy Dataset 1 (Validation) & full gradient descent & 1e-5 &   0.01  & 0.003 & 0.003 & 0.003 & 0.003 \\
Toy Dataset 1 (Validation) & full gradient descent & 1e-3 &  0.063 & 0.003 & 0.003 & 0.003 & 0.007 \\
Toy Dataset 1 (Validation) & full gradient descent & 1e-1 &   0.667 & 0.667 & 0.667 & 0.667 & 0.667 \\
\midrule
Toy Dataset 1 (Training) & SGD & 0 &       \bf{0.003} & 0.003 & 0.003 & 0.003 & 0.003 \\
Toy Dataset 1 (Training) & SGD & 1e-5 &   0.043 & 0     & 0.003 & 0.003 & 0     \\
Toy Dataset 1 (Training) & SGD & 1e-3 &   0.117 & 0     & 0.003 & 0.003 & 0.003 \\
Toy Dataset 1 (Training) & SGD & 1e-1 &   0.667 & 0.667 & 0.667 & 0.667 & 0.667 \\
\midrule
Toy Dataset 1 (Validation) & SGD & 0 &       \bf{0.003} & 0.003 & 0.01  & 0.007 & 0.003 \\
Toy Dataset 1 (Validation) & SGD & 1e-5 &   0.033 & 0.007 & 0.003 & 0.007 & 0.003 \\
Toy Dataset 1 (Validation) & SGD & 1e-3 &   0.097 & 0.013 & 0.013 & 0.013 & 0.013 \\
Toy Dataset 1 (Validation) & SGD & 1e-1 &  0.667 & 0.667 & 0.667 & 0.667 & 0.667 \\
\midrule
Toy Dataset 2 (Training) & full gradient descent & 0 &      0.36  & 0.063 & 0.047 & 0.05  & 0.027 \\
Toy Dataset 2 (Training) & full gradient descent & 1e-5 &   0.397 & 0.063 & 0.067 & 0.063 & 0.067 \\
Toy Dataset 2 (Training) & full gradient descent & 1e-3 &  0.413 & \bf{0.06}  & 0.06  & 0.06  & 0.06  \\
Toy Dataset 2 (Training) & full gradient descent & 1e-1 &  0.667 & 0.667 & 0.667 & 0.667 & 0.667 \\
\midrule
Toy Dataset 2 (Validation) & full gradient descent & 0 &      0.343 & 0.07  & 0.093 & 0.1   & 0.107 \\
Toy Dataset 2 (Validation) & full gradient descent & 1e-5 &   0.39  & 0.073 & 0.07  & 0.073 & 0.073 \\
Toy Dataset 2 (Validation) & full gradient descent & 1e-3 &  0.38  & \bf{0.067} & 0.067 & 0.067 & 0.067 \\
Toy Dataset 2 (Validation) & full gradient descent & 1e-1 &  0.667 & 0.667 & 0.667 & 0.667 & 0.667 \\
\midrule
Toy Dataset 2 (Training) & SGD & 0 &       0.363 & 0.073 & 0.053 & 0.05  & 0.06  \\
Toy Dataset 2 (Training) & SGD & 1e-5 &   0.363 & 0.07  & \bf{0.067} & 0.057 & 0.067 \\
Toy Dataset 2 (Training) & SGD & 1e-3 &   0.363 & 0.07  & 0.07  & 0.07  & 0.07  \\
Toy Dataset 2 (Training) & SGD & 1e-1 &   0.667 & 0.667 & 0.667 & 0.667 & 0.667 \\
\midrule
Toy Dataset 2 (Validation) & SGD & 0 &       0.373 & 0.083 & 0.11  & 0.103 & 0.113 \\
Toy Dataset 2 (Validation) & SGD & 1e-5 &   0.373 & 0.087 & \bf{0.077} & 0.08  & 0.09  \\
Toy Dataset 2 (Validation) & SGD & 1e-3 &   0.377 & 0.097 & 0.097 & 0.093 & 0.093 \\
Toy Dataset 2 (Validation) & SGD & 1e-1 &   0.667 & 0.667 & 0.667 & 0.667 & 0.667 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\captionof{table}{Neural Net Classification Error Rates on MNIST dataset for different choices of parameters} 
\centering
\begin{tabular}{llllllllll}
\toprule
Dataset & $lr$ & method & $\lambda$ & $n_1$ = 50 & $n_1$ = 100 & $n_1 = 150$ \\
\midrule
Training & .1 & full gradient descent &  0 & 0     & 0     & \bf{0}     \\
Training & .1 & full gradient descent & 1e-3 & 0.007 & 0.005 & 0.006 \\
Training & .1 & full gradient descent & 1e-2 & 0.069 & 0.069 & 0.074 \\
Training & .1 & full gradient descent & 1e-1 & 0.812 & 0.812 & 0.812 \\
\midrule
Validation & .1 & full gradient descent &  0 & 0.068 & 0.078 & \bf{0.062} \\
Validation & .1 & full gradient descent & 1e-3 &  0.064 & 0.07  & 0.062 \\
Validation & .1 & full gradient descent & 1e-2 & 0.072 & 0.078 & 0.078 \\
Validation & .1 & full gradient descent & 1e-1 & 0.822 & 0.822 & 0.822 \\
\midrule
Training & .1 & SGD &  0 & 0.112 & 0.109 & \bf{0.106} \\
Training & .1 & SGD & 1e-3 & 0.109 & 0.119 & 0.114 \\
Training & .1 & SGD & 1e-2 & 0.13  & 0.132 & 0.131 \\
Training & .1 & SGD & 1e-1 & 0.683 & 0.703 & 0.78  \\
\midrule
Validation & .1 & SGD &  0 & 0.09  & 0.1   & \bf{0.086} \\
Validation & .1 & SGD & 1e-3 & 0.092 & 0.09  & 0.098 \\
Validation & .1 & SGD & 1e-2 & 0.122 & 0.122 & 0.12  \\
Validation & .1 & SGD & 1e-1 & 0.68  & 0.698 & 0.762 \\
\midrule
Training & .01 & full gradient descent &  0 & 0.084 & 0.064 & 0.057 \\
Training & .01 & full gradient descent &  1e-3 & 0.076 & 0.067 & \bf{0.056} \\
Training & .01 & full gradient descent &  1e-2 & 0.094 & 0.087 & 0.081 \\
Training & .01 & full gradient descent & 1e-1 & 0.663 & 0.66  & 0.66  \\
\midrule
Validation & .01 & full gradient descent &  0 & 0.09  & 0.076 & 0.08  \\
Validation & .01 & full gradient descent & 1e-3 & 0.102 & 0.074 & \bf{0.07}  \\
Validation & .01 & full gradient descent & 1e-2 & 0.088 & 0.08  & 0.076 \\
Validation & .01 & full gradient descent & 1e-1 & 0.674 & 0.672 & 0.672 \\
\midrule
Training &.01 & SGD &  0 & 0.14  & 0.122 & 0.115 \\
Training &.01 & SGD & 1e-3 & 0.153 & 0.132 & \bf{0.124} \\
Training &.01 & SGD & 1e-2 & 0.153 & 0.152 & 0.138 \\
Training &.01 & SGD & 1e-1 & 0.629 & 0.545 & 0.511 \\
\midrule
Validation & .01 & SGD &  0 & 0.14  & 0.116 & 0.118 \\
Validation & .01 & SGD & 1e-3 & 0.136 & 0.126 & \bf{0.108} \\
Validation & .01 & SGD & 1e-2 & 0.128 & 0.142 & 0.124 \\
Validation & .01 & SGD & 1e-1 & 0.622 & 0.548 & 0.504 \\
\bottomrule
\end{tabular}
\end{table}
